Enhancing Forecast Reconciliation: A Study of Alternative Covariance Estimators

### 2025-08-01 literature/paper_draft.qmd
final touch for Milestone 4

---
title: "Enhancing Forecast Reconciliation: A Study of Alternative Covariance Estimators"
author: Vincent Su
format: 
  pdf:
    include-in-header:
      text: |
        <!-- \usepackage{amsmath} -->
        <!-- \usepackage{mathspec} -->
        \usepackage{algorithm}
        \usepackage{algpseudocode}
        \usepackage[colorlinks=true, linkcolor=blue, citecolor=blue, urlcolor=blue]{hyperref}
        \usepackage{array}
    mathspec: true
    number-sections: true
# crossref:
#   custom:
#     - kind: float
#       key: alg
#       reference-prefix: Algorithm
#       caption-prefix: Algorithm
#       # for PDF output only, tell LaTeX to use the `algorithm` env:
#       latex-env: algorithm
execute:
  cache: false
  echo: false
  warning: false
bibliography: D:/Github/Recon_Honours_Thesis/references.bib
# bibliographystyle: apa
csl: D:/Github/Recon_Honours_Thesis/apa.csl
editor_options: 
  chunk_output_type: console
---

@@

# Theoretical Framework

@@

# Covariance Estimation Approaches

@@

# Simulation

@@

# Forecasting Australian Domestics Tourism

>>>>

---
title: "Enhancing Forecast Reconciliation: A Study of Alternative Covariance Estimators"
author: 
  - Vincent Su
  - Shanika Wickramasuriya (supv.)
  - George Athanasopoulos (supv.)
format: 
  pdf:
    include-in-header:
      text: |
        <!-- \usepackage{amsmath} -->
        <!-- \usepackage{mathspec} -->
        \usepackage{algorithm}
        \usepackage{algpseudocode}
        \usepackage[colorlinks=true, linkcolor=blue, citecolor=blue, urlcolor=blue]{hyperref}
        \usepackage{array}
    mathspec: true
    number-sections: true
# crossref:
#   custom:
#     - kind: float
#       key: alg
#       reference-prefix: Algorithm
#       caption-prefix: Algorithm
#       # for PDF output only, tell LaTeX to use the `algorithm` env:
#       latex-env: algorithm
execute:
  cache: false
  echo: false
  warning: false
bibliography: D:/Github/Recon_Honours_Thesis/references.bib
# bibliographystyle: apa
csl: D:/Github/Recon_Honours_Thesis/apa.csl
editor_options: 
  chunk_output_type: console
---

@@

# Theoretical Framework {#sec-pre-theory}

@@

# Covariance Estimation Approaches {#sec-cov-est}

@@

# Simulation Design {#sec-simulation}

@@

# Forecasting Australian Domestics Tourism {#sec-empirical}
